Boutiques: a flexible framework to integrate command-line applications in computing platforms

### 2018-02-20 boutiquespaper.tex
Updates requested by the editor

@@

%%%% Commands %%%%

\newcommand{\note}[2]{\pdfmargincomment[color=yellow,author=#1,open=true]{#2}}
\newcommand{\todo}[1]{\color{red}TODO: #1\color{black}}
\newcommand{\boutiques}{Boutiques\xspace}
\newcommand{\notimplementedyet}[1]{\color{blue}\emph{#1}\footnote{Still needs to be implemented}\color{black}\xspace}
\algrenewcommand{\algorithmiccomment}[1]{\# \textit{#1}} % so that comments in algorithms are preprended by '#' instead of a small right arrow

@@

>>>>

\journal{gigascience}

@@

%%%% Commands %%%%
\newcommand{\boutiques}{Boutiques\xspace}
\algrenewcommand{\algorithmiccomment}[1]{\# \textit{#1}} % so that comments in algorithms are preprended by '#' instead of a small right arrow

@@

\section{Availability of supporting source code and requirements}
\begin{itemize}
\item Project name: Boutiques
\item Project RRID: SCR\_016073
\item Project home page: \url{http://boutiques.github.io}
\item Operating system(s): Platform independent
\item Programming language: Python and JSON schema
\item Other requirements: None
\item License: MIT
\end{itemize}

\section{Availability of supporting data}

Boutiques is available on GitHub (\url{https://github.com/boutiques/boutiques}) and Zenodo~\cite{tristan_glatard_2018_1164290}. This paper is based on release 0.5.5.
